---
title: MISA length analysis
author: Sean Browning <sbrowning (at) cdc (dot) gov>
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        df_print: paged
        toc: Yes
        toc_float: Yes
        theme: readable
---

```{r knit_opts, include=FALSE}
knitr::opts_chunk$set(
    include = TRUE,
    echo = FALSE, warning = FALSE, message = FALSE,
    dev = "CairoSVG",
    knitr.kable.NA = ""
)
```

```{r lib}
library(dplyr)
library(Cairo)
library(readr)
library(ggplot2)
library(ggthemr)
library(arrow)

ggthemr("fresh")

# === Helperfun to summarize quantiles
quant_df <- function(...) {
    quant_names <- paste0("q", 100 * eval(match.call(expand.dots = FALSE)$...[[2]]))

    x <- as.list(quantile(...))
    names(x) <- quant_names

    return(as.data.frame(x))
}
```

## Data In
```{r data_in}
# === Path handling
# If we're knitting, use one directory down
if (isTRUE(getOption("knitr.in.progress"))) {
    data_dir <- file.path("..", "data")
    output_dir <- file.path("..", "output")
} else {
    data_dir <- file.path("data")
    output_dir <- file.path("output")
}

cohort <- read_csv(file.path(output_dir, "cohort.csv"))

# Reading in targets
# ...also adding medrec-level misa label
icu_targets <- read_csv(file.path(data_dir, "targets", "icu_targets.csv")) %>%
    group_by(medrec_key) %>%
    mutate(misa_medrec = sum(misa_filled, na.rm = TRUE) > 0) %>%
    ungroup()

id_df <- open_dataset(file.path(data_dir, "data", "vw_covid_pat_all")) %>%
    filter(medrec_key %in% icu_targets[["medrec_key"]]) %>%
    arrange(medrec_key, disc_mon, disc_mon_seq) %>%
    collect()
```

We have to read in the pat_all table, since the covid_pat table only contains covid inpatient visits.  
Using `arrow`, we can pre-filter and sort on read-in since this is a pretty large dataset.  

This is prefiltered to the icu_targets, which have the following criteria on the medrec level:  
- at least 1 covid inpatient visit  
    - pat_type == 8  
    - age > 21  
    - admission date >= March 1, 2020  

## Trimming to first COVID visit  

We're already sorted to discharge month, and sequence.  

We'll want to calculate a cumsum of covid visits by medrec to then slice those visits that occur after the first covid inpatient visit.  


```{r trimming}
trimmed_id <- id_df %>%
    group_by(medrec_key) %>%
    mutate(
        # READ: Count how many visits match this criteria starting from index
        visit_count = n(),
        inpat_covid_visit = adm_mon >= 2020103 & covid_visit & pat_type == 8 & i_o_ind == "I" & age >= 21,
        cum_inp_covid_visit = cumsum(inpat_covid_visit),
        total_inp_covid_visits = sum(inpat_covid_visit)
    ) %>%
    ungroup()
```

## Vis {.tabset }

### Inpatient COVID-19 Visits by medrec

Pretty few persons are treated inpatient for COVID-19 >1x (or that we can tell based on their medrec_key).  

```{r vis1, fig.width=7}
n_medrec <- length(unique(trimmed_id[["medrec_key"]]))

trimmed_id %>%
    distinct(medrec_key, total_inp_covid_visits) %>%
    count(total_inp_covid_visits) %>%
    mutate(lab = sprintf("%s (%.2f%%)", format(n, big.mark = ","), 100 * (n / sum(n)))) %>%
    ggplot(aes(x = total_inp_covid_visits, y = n)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = lab), nudge_y = 5000) +
    labs(
        x = "Number of Inpatient COVID-19 visits",
        y = "Persons (n)",
        title = "Number of inpatient visits by Medical Record ID",
        subtitle = sprintf("n = %s", format(n_medrec, big.mark = ","))
    )
```

### Total visits by medrec (pre-slice)

i.e. before we trim to only visits prior to the first inpatient COVID-19 visits, how many visits are there in the database by medrec.  

```{r visits_by_medrec, fig.width=7}
pre_trim_visit_count <- trimmed_id %>%
    distinct(medrec_key, visit_count) %>%
    left_join(
        distinct(icu_targets, medrec_key, status),
        by = "medrec_key"
    ) %>%
    mutate(status = c("MISA", "Severe COVID", "Non-Severe COVID")[status + 1])

pre_trim_visit_count %>%
    ggplot(aes(x = visit_count, y = status, group = status, fill = status)) +
    geom_boxplot() +
    labs(
        x = "Number of Inpatient COVID-19 visits",
        y = "Status Type",
        title = "All visits by Medical Record ID",
        subtitle = sprintf("n = %s", format(n_medrec, big.mark = ","))
    )
```

```{r pre_slice fivenum}
bind_rows(
    pre_trim_visit_count %>%
        group_by(status) %>%
        summarize(quant_df(visit_count, c(0.1, 0.25, 0.5, 0.75, 0.9))),
    pre_trim_visit_count %>%
        summarize(
            status = "Overall",
            quant_df(visit_count, c(0.1, 0.25, 0.5, 0.75, 0.9))
        )
)
```

### Total visits by medrec (post-slice)

This is virtually identical since there are few people with multiple inpatient visits for COVID-19.  

```{r slice, fig.width=7}
# Slice down only to the first inpatient covid vist (or prior)
sliced_id <- trimmed_id %>%
    filter(cum_inp_covid_visit < 1 | (inpat_covid_visit & cum_inp_covid_visit == 1)) %>%
    group_by(medrec_key) %>%
    mutate(visit_count = n()) %>%
    ungroup()

post_trim_visit_count <- sliced_id %>%
    distinct(medrec_key, visit_count) %>%
    left_join(
        distinct(icu_targets, medrec_key, status),
        by = "medrec_key"
    ) %>%
    mutate(status = c("MISA", "Severe COVID", "Non-Severe COVID")[status + 1])

post_trim_visit_count %>%
    ggplot(aes(x = visit_count, y = status, group = status, fill = status)) +
    geom_boxplot() +
    labs(
        x = "Number of Inpatient COVID-19 visits",
        y = "Status Type",
        title = "All visits by Medical Record ID, post trim",
        subtitle = sprintf("n = %s", format(n_medrec, big.mark = ","))
    )
```

```{r slice fivenum}
bind_rows(
    post_trim_visit_count %>%
        group_by(status) %>%
        summarize(quant_df(visit_count, c(0.1, 0.25, 0.5, 0.75, 0.9))),
    post_trim_visit_count %>%
        summarize(
            status = "Overall",
            quant_df(visit_count, c(0.1, 0.25, 0.5, 0.75, 0.9))
        )
)
```

### Theoretical days of observation (post-slice)

i.e. total LOS where we might have information.

**This includes only the first day of the first covid visit (or the final visit in the sequence).**   

Hopefully this helps us get at how many days we ought to lookback.  


```{r slice LOS}
post_slice_total_los <- sliced_id %>%
    group_by(medrec_key) %>%
    mutate(total_los = sum(los, na.rm = TRUE) - (inpat_covid_visit * (los - 1))) %>%
    filter(inpat_covid_visit) %>%
    distinct(medrec_key, total_los) %>%
    ungroup() %>%
    left_join(
        distinct(icu_targets, medrec_key, status),
        by = "medrec_key"
    ) %>%
    mutate(status = c("MISA", "Severe COVID", "Non-Severe COVID")[status + 1])

post_slice_total_los %>%
    ggplot(aes(x = total_los, y = status, group = status, fill = status)) +
    geom_boxplot() +
    labs(
        x = "Total Length-of-stay",
        y = "Status Type",
        title = "Total LOS by Medical Record ID, post trim",
        subtitle = sprintf("n = %s", format(n_medrec, big.mark = ","))
    )
```

```{r slice LOS fivenum}
bind_rows(
    post_slice_total_los %>%
        group_by(status) %>%
        summarize(quant_df(total_los, c(0.1, 0.25, 0.5, 0.75, 0.9, 0.95))),
    post_slice_total_los %>%
        summarize(
            status = "Overall",
            quant_df(total_los, c(0.1, 0.25, 0.5, 0.75, 0.9, 0.95))
        )
)
```

### Calendar time (post-slice)

```{r calendar time}
post_slice_calendar_time <- sliced_id %>%
    filter(inpat_covid_visit) %>%
    distinct(medrec_key, days_from_index) %>%
    left_join(
        distinct(icu_targets, medrec_key, status),
        by = "medrec_key"
    ) %>%
    mutate(status = c("MISA", "Severe COVID", "Non-Severe COVID")[status + 1])

post_slice_calendar_time %>%
    ggplot(aes(x = days_from_index, y = status, group = status, fill = status)) +
    geom_boxplot() +
    labs(
        x = "Time from index (d)",
        y = "Status Type",
        title = "Total Calendar time from Index by Medical Record ID, post trim",
        subtitle = sprintf("n = %s", format(n_medrec, big.mark = ","))
    )
```

```{r slice calendar time fivenum}
bind_rows(
    post_slice_calendar_time %>%
        group_by(status) %>%
        summarize(quant_df(days_from_index, c(0.1, 0.25, 0.5, 0.75, 0.9))),
    post_slice_calendar_time %>%
        summarize(
            status = "Overall",
            quant_df(days_from_index, c(0.1, 0.25, 0.5, 0.75, 0.9))
        )
)
```
